\documentclass[10pt]{article}

\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\usepackage{blindtext}
\usepackage{color}

\textheight 9.5 in
\textwidth 7 in
\hoffset -1.1 in
\voffset -.75 in

\headheight 36pt
\headsep .25in

\newcommand{\headskip}{\vspace{.075in}}
\newcommand{\miniskip}{\vspace{.03in}}
\renewcommand{\headrulewidth}{0pt}

\newcommand{\heading}[1]{
  \miniskip
  \noindent {\bf #1} \vspace{.05in} \hrule
  \headskip
}

\newcommand{\subheading}[2]{
  \noindent {\bf #1} \hfill \emph{#2}
}

\newenvironment{compactitemize} {
  \begin{itemize}[rightmargin=.25in, topsep=0pt]
    \setlength{\itemsep}{0pt}
    \setlength{\parsep}{0pt}
    \setlength{\parskip}{0pt}
} {
  \end{itemize}
}

\begin{document}

\pagestyle{fancy}
\fancyfoot{}
\fancyhead{}
\fancyhead[L]{111 Trowbridge St, Apt 9\\
  Cambridge, MA 02138
}

\fancyhead[C]{\bf {\huge Forest Trimble}}
\fancyhead[R]{(774) 545-9538\\
  trimble.forest@gmail.com
}


\heading{EDUCATION}

\noindent {\bf Rensselaer Polytechnic Institute, Troy, NY} \hfill
\emph{2011-2014}\\
\miniskip
\noindent \emph{B.S. Computer Science and Mathematics of Computation, Summa
Cum Laude, 3.93 GPA} \\
\miniskip
{\bf Acton Boxborough Regional High School, Acton, MA} \hfill
\emph{2007-2011}

\heading{WORK EXPERIENCE}

\subheading{Amazon.com}{Cambridge, MA}

\subheading{Software Development Engineer II - Digital Products}{July 2014 - Present}

\noindent \emph{Text Recognition experience for Firefly}
\begin{compactitemize}
\item Participated in a hack-day project for business card recognition
  that was successful enough to spur the creation of a new team to pursue
  the project more seriously.
\item Delivered NLU algorithms for four new word types, doubling the available
  types.
\item Implemented a positional homography between images based on a
  linear regression of text positions, and prototyped an algorithm
  that would take a set of free-form text zones and the homography to
  produce greatest-confidence zones over the body of text.
\end{compactitemize}

\noindent \emph{Build infrastructure improvements}
\begin{compactitemize}
\item Independently recognized the need for a state caching
  system for our build tools and designed and implemented a suite of
  bash scripts to do so, outside of my sprint deliverables. This
  reduced build times by as much as 10x, causing massive increases in
  developer productivity.
\item Drove improvements in quality standards, driving the adoption of
  static analysis tools and maintaining the statistically highest code
  review standards on my team.
\item Migrated a set of over 30 packages from ANT to Gradle, bringing
  our build infrastructure up to date with the latest Android technology.
\item Contributed multi-module build functionality to company-wide
  gradle add-ons, allowing teams across Amazon to produce Android apks
  that are tested by multiple instrumentation apks.
\end{compactitemize}

\noindent \emph{Prototype device efforts}
\begin{compactitemize}
\item Architected an extensible framework for displaying textual
  information to the user with a given priority, timeout behavior, and
  display behavior that hooks into our pipeline of events to broadcast
  updates.
\item Created a robust camera stack that utilizes RxJava to send events when a
  camera frame meets requirements. This stack needed to cope with some
  implementation issues of incomplete support from our hardware vendor, which I
  resolved by creating a mapping between two asynchronous streams of data using
  a custom data structure that automatically removes and closes items when they
  cannot be matched to cope with memory requirements.
\end{compactitemize}

\subheading{Software Development Engineer Intern - Firefly}{May - August 2013}

\begin{compactitemize}
\item Architected a largely regex-based classification and extraction service
  for a new word type through our existing text recognition infrastructure. This
  word type was the first to span multiple lines of text.
\item Multiline classification was wrought with problems due to
  failures in the underlying zoning algorithms. I simplified the whole
  approach by breaking down classification into multiple single-line
  procedures and an extraction method that could span multiple zones
  of unclassified text.
\end{compactitemize}

\subheading{Rensselaer Center for Open Source Software}{Troy, NY}

\subheading{Founder/Developer - King Me}{September 2013 - May 2014}

\noindent \emph{This is a personal project without managerial structure that I
  got funding for through RPI. I created this project with two ideas to improve
  over existing ride trackers: automated cycling route generation and
  challenges, where you would challenge another athlete to who could perform the
  best in a few day period using indices like power, heart rate, and segments.}
\begin{compactitemize}
\item Ideated and implemented a basic algorithm for generating routes by
  approximating a circle of a given distance using pyroute to encapsulate Open
  Street Maps data.
\item Created a minimal Android app to track relevant ride data.
\item Coordinated 5 other developers that were working on the web interface and
  the Android application.
\end{compactitemize}

\subheading{SEPATON}{Marlborough, MA}

\subheading{Software Developer Intern}{May - August 2012}

\begin{compactitemize}
\item Wrote a GUI using Qt and C++ for troubleshooting and analyzing the core
  deduplication algorithm.
\item The GUI needed to be able to show this information retroactively on
  customer databases, so I implemented a log parsing utility that converted the
  human-readable (though not particularly human-useful) output of the logs into
  data that could be displayed by the GUI.
\end{compactitemize}

\end{document}
